Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-10-17 draft.tex
getting caught up in making HKR work, for lots of issues

@@

There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^\bu \otimes V$ with differential $\d_{dR} + \partial$,
which is a soft replacement for the locally constant sheaf $V$.
In the same way, we define the factorization algebra 
\[
F_A = (\Sym((\Omega^\bu)^* \otimes V ), \d_{dR} + \partial) 
\]
which is manifestly commutative and is quasi-isomorphic to $A$ on every disk.
Hence $F_A$ is a commutative, locally constant factorization algebra that models~$A$.

>>>>

\owen{This is really turning into a mess.}

@@

There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^\bu$ with differential $\d_{dR}$,
which is a soft replacement for the locally constant sheaf $\RR$.
Taking duals, we get a cosheaf.
In the same way, we define the factorization algebra 
\[
F_A = (\Sym((\Omega^\bu)^* \otimes V ), \d_{dR} + \partial) 
\]
which is manifestly commutative and is quasi-isomorphic to $A$ on every disk.
Hence $F_A$ is a commutative, locally constant factorization algebra that models~$A$.
